Monday, July 22nd
\begin{itemize}
    \item Came up with conjecture for $F_p^k$ terms (extending Lenart Maeno) in Grassmanians
    \item Confirmed conjecture for $Gr(1, 5), Gr(2, 5), Gr(3, 5), Gr(4, 5)$ and the corresponding Chevalley relations (very excited as this could be new!)
\end{itemize}

Tuesday, July 23rd
\begin{itemize}
    \item Met with Linda to discuss progress on guesses/Grassmanians and next steps (testing in larger ambient spaces/automating the process)
    \item Discovered first working guesses for $F_p^k$ in $Fl(1, 2, 4)$ and $Fl(1, 3, 4)$ -- all Chevalley satisfied!
    \item Next step: test Grassmanian conjecture against $Gr(3, 6), Gr(4, 7), Gr(4, 8)$ (create way to automate this process), and above guesses for $Fl(2, 3, 4)$ and other partial flags (again, find a way to automate this process).
\end{itemize}

Wednesday, July 24th
\begin{itemize}
    \item Working on automizing Chevalley relation tests
    \item Coded up $F_p^k$ conjecture for any partial flag, and corresponding Grothendieck functions
    \item Checked that relations are satisfied for $Fl(1, 2, 3, 5)$
\end{itemize}

Thursday. July 25th
\begin{itemize}
    \item Further work on optimizing Chevalley checking
    \item Possible next steps \& Meeting Notes
    \begin{itemize}
        \item Find analogous recursions for partial flags, mirroring Lenart-Maeno -- recursions can give you Pieri rules
        \item Try to show current presentations are consistent with Wu/Sharpe/Xu. Hopefully their recursions match up with our recursions. Recursions may or may not be enough to prove Chevalley
        \item So...have recursions on the f's. Use that to choose they fit the relations.
        \item Zoe: work on relations. Also come up with a nice looking definition of the F's. F(p,n,k) in terms of F(p,n-1,k). 
    \end{itemize} 
\end{itemize}

Friday, July 26 (Goals/Further Directions of Work)
\begin{itemize}
    \item Write our definition in terms of the elementary symmetrics. $F_p^{n_k}$ can be written in terms of $\tau_i^1, \ldots, \tau_j^k$ and $q$'s. (Zoe)
    \item We should be able to write a $F$ for given flag in terms of the elementary symmetrics (elementary in $(1-x_i)$). Can do elementaries per each block. (Zoe)
    \item Linda is going to write conjecture in terms of polynomials (versus in terms of the wedge product). We will then hopefully use our/LM recursions to prove it
    \item Duality. Might want to show our guesses are consistent with the isomorphism between dual flags (LM do this, when they divide by (1-$x_i$) or something)
\end{itemize}